\emph{Light Exposure Behavior Assessment (LEBA)}: Development of a novel instrument to capture light exposure-related behaviours

### 2022-01-09 manuscript.Rmd

write.csv(full.map, "Table_raw/map_stat")
```
Scree plot ( Figure \@ref(fig:facIdFig)) suggested a six-factor solution. Horn's parallel analysis [@hornRationaleTestNumber1965] with 500 iterations also indicated a six-factor solution. However, the minimum average partial (MAP) method (Table \@ref(tab:factormp)) [@velicerDeterminingNumberComponents1976] and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:facIdFig)) suggested a five-factor solution. As a result, we tested both five-factor and six-factor solutions.
```{r factors, include=F}
fator <- cowplot::plot_grid(parallel, scree.plot,Hull, 
                   labels = "AUTO",
                   ncol=1, 
                  align = "v", 
                  label_size = 15,
                  label_fontfamily = "Arial",
                  label_fontface = "plain")
ggsave("Manuscript.figures/factors.png",fator, width = 6, height = 12, dpi = 1200)
```

@@

```{r EFAplot, fig.align='center', fig.cap='(A) Five Factor Solution obtained in Exploratory Factor Analysis. The factor loadings ranged between .49-.99 (B) Histogram of nonredundent residula correlations indicated 26% correlations are higher than absolute value of .05 indicating a possible under factoring', warning=FALSE,  results='asis'}

@@

```{r figcfa, fig.cap = "Five Factor  Model of LEBA obtained by Confirmatory Factor Analysis. By allowing item pain 41 & 30 to covary their error variance our model attained the best fit.", out.height="150%", out.width="100%", dpi=1200,  warning=FALSE}
#library(semPlot)

@@

F5.itemplots <- cowplot::plot_grid(F5.iteminfo.1,F5.iteminfo.2, F5.iteminfo.3,
                                   F5.iteminfo.4,F5.iteminfo.5,
                   labels = "AUTO",
                     align="v",
                     ncol = 2,
                     label_size = 12,
                     label_fontfamily = "Arial",
                     label_fontface = "plain")
ggsave("Manuscript.figures/F5.itemplots.png",F5.itemplots, width = 10, height = 12, dpi = 1200, bg = "white")
```

@@

ICC2 <- cowplot::plot_grid(vic.iic2 , agg.iic2,  labels = "AUTO",ncol=2, label_size = 15,align = "v")
ggsave("Figures/ICC2.jpeg",ICC2 , width = 12, height = 8, dpi = 1200, bg = "white")

>>>>

write.csv(full.map, "Table_raw/map_stat")
```
Scree plot ( Figure \@ref(fig:facIdFig)) suggested a six-factor solution. Horn's parallel analysis [@hornRationaleTestNumber1965] with 500 iterations also indicated a six-factor solution. However, the minimum average partial (MAP) method (Table \@ref(tab:factormp)) [@velicerDeterminingNumberComponents1976] and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:facIdFig)) suggested a five-factor solution. As a result, we tested both five-factor and six-factor solutions.
```{r factors, include=F}
fator <- cowplot::plot_grid(parallel, scree.plot,Hull, 
                   labels = "AUTO",
                   ncol=1, 
                  align = "v", 
                  label_fontfamily = "Arial",
                  label_fontface = "plain")
ggsave("Manuscript.figures/factors.png",fator, width = 6, height = 12, dpi = 1200)
```

@@

```{r EFAplot, fig.align='center', fig.cap='(A) Five Factor Solution obtained in Exploratory Factor Analysis (B) Histogram of nonredundent residula correlations', warning=FALSE,  results='asis'}

@@

```{r figcfa, fig.cap = "Five Factor  Model of LEBA obtained by Confirmatory Factor Analysis. By allowing item pain 41 & 30 to covary their error variance our model attained the best fit.", out.height="150%", out.width="100%", dpi=1200,  warning=FALSE}

#library(semPlot)

@@

F5.itemplots <- cowplot::plot_grid(F5.iteminfo.1,F5.iteminfo.2, F5.iteminfo.3,
                                   F5.iteminfo.4,F5.iteminfo.5,
                   labels = "AUTO",
                     align="v",
                     ncol = 2,
                     label_size = 12,
                     label_fontfamily = "Arial",
                     label_fontface = "plain")
ggsave("Manuscript.figures/F5.itemplots.png",F5.itemplots, width = 10, height = 12, dpi = 1200, bg = "white")

@@

ICC2 <- cowplot::plot_grid(vic.iic2 , agg.iic2,  labels = "AUTO",ncol=2, label_size = 15,align = "v")
ggsave("Figures/ICC2.jpeg",ICC2 , width = 12, height = 8, dpi = 1200, bg = "white")
```
